\chapter{Bibliografía}
\begin{thebibliography}{99}

\bibitem{Robotics} Online. Systems, Intelligence, Robotics and Perception, Pontificia Universidad Javeriana Bogotá http://www.gruposirp.org/sirp/wiki/doku.php http://gruposirp.org/sirp/sirp-home.html WebSite 2011.

\bibitem{ALM} Presentación Kinect Bruno Capuano Visual Studio ALM
https://mvp.support.microsoft.com/profile=800D1522-8788-4A34-8985-233DBBF2A40A Conference Cidetec IPN 2011 cortesía Ing. Naím Rivera.

\bibitem{OpenNI} Online. OpenNI \texttrademark. http://75.98.78.94/About.aspx

\bibitem{Intel} Open Source Computer Vision Library. Reference Manual. Edic. Intel Corporation.

\bibitem{Theodoquidis} \textquotedblleft Pattern Recognition\textquotedblright Sergios Theodoquidis, Konstantinos Kourtroumbus Ed. Acaemic Press 2° Edición 2003.

\bibitem{Shulcloper} \textquotedblleft Reconocimiento de Patrones: Enfoque Lógico Combinatorio\textquotedblright José Ruiz Shulcloper Ed. Instituto Politécnico Nacional.

\bibitem{Fiducials} \textquotedblleft The Design and Evolution of Fiducials for the reacTIVision System\textquotedblright, Ross Bencina and Martin Kaltenbrunner, Universitat Pompeu Fabra, Barcelona, España, 2005.

\bibitem{reacTIVison} Online. reacTIVison, http://reactivision.sourceforge.net/

\bibitem{QR} Online. QR code, versions 1 - 40. http://www.denso-wave.com/qrcode/vertable1-e.html

\bibitem{Otsu} Online. Otsu Thresholding,  The Lab bookpages http://www.labbookpages.co.uk/software/imgProc/otsuThreshold.html

\bibitem{ZXing} Online. ZXing web page. http://code.google.com/p/zxing/

\bibitem{ARToolkit} Online.  ARToolkit Documentation. http://www.hitl.washington.edu/artoolkit/documentation/userarwork.htm

\bibitem{Pressman} Roger S. Pressman (adaptado por Darrel Ince), Ingeniería del Software un enfoque práctico, 5ta ed. Ed. McGraw-Hill, pp. 23-24.

\bibitem{carpiano} Síndrome del túnel carpiano | Causas y factores de riesgo http://familydoctor.org/familydoctor/es/diseases-conditions/carpal-tunnel-syndrome/causes-risk-factors.html

\bibitem{Tracking} Online. Hand Tracking (Kinect with OpenCV and OpenNI). http://www.youtube.com/watch?v=qNH\_MqqOPX0

\bibitem{Mapping} Online. Kinect Active Projection Mapping. http://www.youtube.com/watch?v=hkHUGxP3ecI

\bibitem{Freiberg} Online. Technical University Bergakademie Freiberg http://www.informatik.tu-freiberg.de/

\bibitem{capas} Online. Arquitectura basada en capas. Posted on May 26, 2009 by Juan Peláez
http://www.juanpelaez.com/geek-stuff/arquitectura/arquitectura-basada-en-capas/

\bibitem{Layer} Online. Estilo arquitectural en capas (N-Layer)
http://www.ecured.cu/index.php/Estilo\_arquitectural\_en\_capas\_28N-Layer29

\bibitem{Belkasim} \textquotedblleft Image Description Using Moments\textquotedblright, Dr. S. Belkasim.

\bibitem{Wavelet} \textquotedblleft Momentos Wavelet del Tipo B-Spline Cùbicos para Clasificación de Objetos\textquotedblright, Judith Pérez Marcial, Benemérita Universidad Autónoma de Puebla, 2005.

\bibitem{upenn} Online. Manual de referencia OpenCV. http://www.seas.upenn.edu/~bensapp/opencvdocs/ref/opencvref\_cv.htm

\bibitem{Parker} J. R. Parker., Algorithms for Image Processing and Computer Vision, Wiley,1997.

\bibitem{tales} Online. \textquotedblleft Técnicas de procesamiento digital de imágenes y reconocimiento de patrones.\textquotedblright http://catarina.udlap.mx/u\_dl\_a/tales/documentos/lis/nieto\_b\_d/capitulo2.pdf

\bibitem{Quilmes} Online \textquotedblleft Segmentación por Umbralización\textquotedblright, Universidad Nacional de Quilmes, 2005
http://iaci.unq.edu.ar/materias/vision/archivos/apuntes/SegmentaciC3B3n20por20umbralizaciC3B3n20-20MC3A9todo20de20Otsu.pdf

\bibitem{Ekow} \textquotedblleft Optimizing Connected Component Labeling Algorithms\textquotedblright Kensheng Wu, Ekow Otoo and Arie Shoshani, Lawrence Berkeley National Laboratory, Berkeley, CA, USA.

\bibitem{Prueba} Online Prueba de Programas José A. Mañas 16 de marzo, 1994
http://www.lab.dit.upm.es/~lprg/material/apuntes/pruebas/testing.htmls22 
\end{thebibliography}
